Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-06-30 article.tex
new graph to compare different flavour of the model (with or without the trade innovation process)

\todo{make the figure and comment the line}
\begin{figure}[h]
	\begin{center}
		\begin{tabular}{cc}
		\includegraphics[width=6cm]{img/2SetupDistrib.pdf} &
%		\includegraphics[width=6cm]{img/InnovationAndNeutralDistrib.pdf}
		\\
		a) & b) \\
		\end{tabular}

	\end{center}
	\caption{Frequency distribution for: a) the neutral and the trading models. Each points represent the mean for 100 runs b) the neutral model and the composed model.}
	\label{fig:2setDi}
\end{figure}

>>>>

\todo{make the figure and comment the line}
\begin{figure}[h]
	\begin{center}
		\begin{tabular}{cc}
		a) & b)  \\
		\includegraphics[width=6cm]{img/2SetupDistribA.pdf} &
		\includegraphics[width=6cm]{img/2SetupDistribB.pdf} \\
		\includegraphics[width=6cm]{img/2SetupDistribC.pdf} &
		\includegraphics[width=6cm]{img/2SetupDistribD.pdf} \\
		c) & d)  \\
		\end{tabular}

	\end{center}
	\caption{Frequency distribution, where each points represent the mean for 100 runs, for: a) the neutral and the trading models.  b) the neutral model and the trading model without the trading innovation process. c) the trading model and the random model with an innovation process similar than the one used in the trade model. d) the trade model and the trade model without the trading innovation process.}
	\label{fig:2setDi}
\end{figure}
